---
title: "simpleRegress"
author: "Ambar Arreola"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

The bears neck is 20 inches around which helps predict 57 inches in length.Looking at the accompanying data it shows that the residual standard error is 5.376 and the r squared is .7524.



## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 



```{r}
MYCHEST <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(MYCHEST)
summary.lm(MYCHEST)
```

The residual standard error is 4.939 and its lower than the previous model which is 5.376 and is better.In addition the R-squared is 0.791 which is higher than the previous model which is  0.7524. So in ranking chest is above neck so we can conclude that chest is better than neck.


```{r}
MYHEADWTH <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(MYHEADWTH)
summary.lm(MYHEADWTH)
```

As for the third model, the residual standard error is 7.32 which is worse. In addition the R-square is now 0.5489 which is also a decline from the previous model. In comparison to the other models the third one is at the bottom of the list. 

